The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-03-01 paper/forestecology.Rmd

The output `growth_scbi` is a single data frame of class `sf` that includes variables `growth`, the average annual growth in DBH (cm y^-1^) for all stems that were alive at both time points, and `geometry`, the `sf` package's encoding of geolocations of type `<POINT>`. Furthermore, the variables that should remain unchanged between censuses appear only once, such as location variables `gx` and `gy`; as well as species-related variables. Variables that should change between censuses are suffixed with `1` and `2` indicating the earlier and later censuses, such as `dbh1/dbh2` and `codes1/codes2`. Site data that does not align with this convention will need to be transformed for use with the `compute_growth()` function. However, in the end all that matters is that the growth of all stems is saved in a data frame of class `sf` and at a minimum the data contains the variables above. TODO: enumerate what these variables are and say if they need exact names

>>>>

The output `growth_scbi` is a single data frame of class `sf` that includes variables `growth`, the average annual growth in DBH (cm y^-1^) for all stems that were alive at both time points, and `geometry`, the `sf` package's encoding of geolocations of type `<POINT>`. Furthermore, the variables that should remain unchanged between censuses appear only once, such as location variables `gx` and `gy`; as well as species-related variables. Variables that should change between censuses are suffixed with `1` and `2` indicating the earlier and later censuses, such as `dbh1/dbh2` and `codes1/codes2`. Site data that does not align with this convention will need to be transformed for use with the `compute_growth()` function. However, in the end, all that matters is that the growth of all stems is saved in a data frame of class `sf` and, at a minimum, the data contains the variables above. TODO: enumerate what these variables are and say if they need exact names
